sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-12-29 doc/paper.Rmd
minor abstract edits

```{r owl-nao, fig.cap="(ref:owl-nao-fig)", out.width="4.1in", fig.align='center'}
owl <- here::here("figs", "owl-nao-effect-2021-12-22.pdf")
if (!file.exists(owl)) {
  download.file("https://www.dropbox.com/sh/p5ydljdycaw9x6n/AAAlaKQArhqP9IHvUSxEq_qWa/owl-nao-effect-2021-12-22.pdf?dl=1", 
    destfile = owl)
}
knitr::include_graphics(owl)
```

>>>>

```{r owl-nao, fig.cap="(ref:owl-nao-fig)", out.width="4.1in", fig.align='center'}
owl <- here::here("figs", "owl-nao-effect-2021-12-22.pdf")
if (!file.exists(owl)) {
  download.file("https://www.dropbox.com/sh/p5ydljdycaw9x6n/AAAlaKQArhqP9IHvUSxEq_qWa/owl-nao-effect-2021-12-22.pdf?dl=0", 
    destfile = owl)
}
knitr::include_graphics(owl)
```
